


[1]  K. H. Looi, "Overcoming challenges to make e-learning a panacea for present and future crises," The International Journal of Information and Learning Technology, vol. 39, no. 3, pp. 227-239, 2022. [Online]. Available: https://0-doi-org.biblioteca-ils.tec.mx/10.1108/IJILT-10-2021-0157



[2] G. Costagliola, A. De Lucia, F. Ferrucci, C. Gravino, and G. Scanniello, "Assessing the usability of a visual tool for the definition of e-learning processes," Journal of Visual Languages and Computing, vol. 19, no. 6, pp. 721-737, 2008. [Online]. Available: https://0-doi-org.biblioteca-ils.tec.mx/10.1016/j.jvlc.2008.01.003


[3] Women TechMakers - Chojnacka R., "How speech recognition works in 60 seconds!," YouTube, [Video], [May 26, 2022]. [Online]. \\
 Available: https://www.youtube.com/watch?v=eQfqcYR3HJo. [Accessed: Dec. 02, 2023].



[4] S. Rella, "Essential Guide to Automatic Speech Recognition Technology," NVIDIA Technical Blog, Aug. 08, 2022. [Online]. \\
Available: https://developer.nvidia.com/blog/essential-guide-to-automatic-speech-recognition-technology/ . [Accessed: Nov. 22, 2023].



[5]  E. Lakomkin, S. Magg, C. Weber, and S. Wermter, "KT-Speech-Crawler: Automatic Dataset Construction for Speech Recognition from YouTube Videos," in Proc. arXiv:1903.09206 [cs.CL], Department of Informatics, Knowledge Technology, University of Hamburg, Vogt-Koelln Str. 30, 22527 Hamburg, Germany, Mar. 2019. [Online]. Available: https://arxiv.org/abs/1903.09206

[6]  H. Liao, E. McDermott, and A. Senior, "Large Scale Deep Neural Network Acoustic Modeling with Semi-Supervised Training Data for YouTube Video Transcription," Google Inc. [Online]. Available: 

[7] C. Alberti and M. Bacchiani, "Automatic captioning in YouTube," Dec. 2009. [Online]. Available: http://googleresearch.blogspot.com/2009/12/automatic-captioning-in-youtube.html. [Accessed: 29-Nov-2023].







[8] D. A. Dahl, Natural Language Understanding with Python, 1st ed. Packt Publishing, [2023]. [E-book]. Available: [ISBN 978-1-80461-342-9]


[9] G. Paass and S. Giesselbach, Foundation Models for Natural Language Processing, Springer, [2022]. [Online]. Available: [https://doi.org/10.1007/978-3-031-23190-2 ]


[10] T. Beysolow II, Applied Natural Language Processing with Python: Implementing Machine Learning and Deep Learning Algorithms for Natural Language Processing, Apress, [2018]. [Online]. Available: [https://doi.org/10.1007/978-1-4842-3733-5]


[11] StanfordOnline, "Stanford XCS224U: NLU I Intro & Evolution of Natural Language Understanding, Pt. 1 I Spring 2023," YouTube, 2023. [Online Video Series]. Available: https://www.youtube.com/watch?v=K_Dh0Sxujuc&list=PLoROMvodv4rOwvldxftJTmoR3kRcWkJBp. [Accessed: 28-Nov-2023].

[12] 

[13] 


[14] Jayawardhana S, "Sequence Models and Recurrent Neural Networks (RNNs)," Towards Data Science, [Publication Date]. [Online]. Available: https://towardsdatascience.com/sequence-models-and-recurrent-neural-networks-rnns-62cadeb4f1e1. [Accessed: 28-Nov-2023].


[15] Kaul S , "Explained: Deep Sequence Modeling with RNN and LSTM," Analytics Vidhya, Medium, [Publication Date]. [Online]. Available: https://medium.com/analytics-vidhya/explained-deep-sequence-modeling-with-rnn-and-lstm-e71521f86036. [Accessed: 28-Nov-2023].

[16]  Giacaglia G, "How transformers work", \textbf{Towards Data Science}, Mar 10, 2019. [Online]. Available: https://towardsdatascience.com/transformers-141e32e69591 [Accessed: Nov. 29, 2023].



[17] R. Merritt, "What Is a Transformer Model?," \textbf{NVIDIA Blogs}, Mar. 25, 2022. [Online]. Available: https://blogs.nvidia.com/blog/what-is-a-transformer-model/. [Accessed: Nov. 29, 2023].

[18] Wikipedia contributors, 'Latent semantic analysis,' Wikipedia, The Free Encyclopedia. [Online]. Available: https://en.wikipedia.org/wiki/Latent_semantic_analysis. [Accessed: 25-Nov-2023].







[19]  Iona, "Latent Semantic Analysis: intuition, math, implementation" Towards Data Science, day-month-year of publication. [Online]. Available: https://towardsdatascience.com/latent-semantic-analysis-intuition-math-implementation-a194aff870f8. [Accessed: 20-Nov-2023].


[20] C. Maklin, "Latent Dirichlet Allocation," Medium, Jan. 1, 2023. [Online]. Available: https://medium.com/@corymaklin/latent-dirichlet-allocation-dfcea0b1fddc. [Accessed: 02-Dec-2023].


[21]  Author(s), David M. Blei, "Introduction to Probabilistic Topic Models,"  [Online]. Available: https://www.eecis.udel.edu/~shatkay/Course/papers/UIntrotoTopicModelsBlei2011-5.pdf. [Accessed: 25-November-2023].



[22] N. S. Gill, J. Kaur, and Suryakant, Hyperautomation with Generative AI, [bpbonline], [London], [2023]

[23]  A. Lo Duca, Data Storytelling with Python Altair and Generative AI. Manning Publications, [E-book] Available: <A. Lo Duca, Data Storytelling with Python Altair and Generative AI. Manning Publications, [E-book] Available: <URL or DOI>
>


[24] W. L. Johnson, "How to Harness Generative AI to Accelerate Human Learning," International Journal of Artificial Intelligence in Education: Official Journal of the International AIED Society, pp. 1-5, 2023. [Online]. Available: https://0-doi-org.biblioteca-ils.tec.mx/10.1007/s40593-023-00367-w







[25]  Wasi, Chat GPT for Dummies: A Quick Introduction to Prompt Engineering!. Leanpub, 2023. [Online]. Available: http://leanpub.com/chatgpt-for-dummies. Accessed on: May 22, 2023.


[26] I. John, The Art of Asking ChatGPT for High-Quality Answers: A Complete Guide to Prompt Engineering Techniques. Nzunda Technologies Limited, [E-book] Available: [URL where the book can be accessed]. [Accessed: date-of-access].




[27] M. Adelson, The ChatGPT Goldrush: Profiting from the AI Revolution Online. [E-book] Available: [URL where the book can be accessed]. [Accessed: date-of-access].





[1] "Education Worldwide." Statista, 2023. [Online]  accessed on [12/04/2023]. Available: https://www.statista.com/topics/7785/education-worldwide/


Related Work 









[20]. Knewton (2021). Knewton Adaptive Learning Platform. Retrieved from https://www.knewton.com/ 





